Abundance/diversity GAM

### 2021-02-27 code/abund_div_GAM.Rmd
back up

>>>>

# Just a quick peak at what would happen if I added a by = year smooth 
```{r}
weighted_fl_abund.qp2 <- bam(total.weighted.flower.cover ~ 
                              s(bb.sp, bs = "re") +
                              s(site, bs = "re") +
                              s(year, bs = "re") +
                              te(yday, elev.mean,
                                 by = year,
                                 bs = c("gp", "tp"),
                                 k = c(5, 5)) +
                              te(yday, elev.mean,
                                 by = bb.sp,
                                 bs = c("gp", "tp"),
                                 k = c(5, 5)),
                            data = filter(weighted_fl_abund, bb.sp != "humi"),
                            family = "quasipoisson",
                            discrete = TRUE,
                            select = TRUE,
                            method = "fREML") %>% getViz(nsim = 500)

check.gamViz(weighted_fl_abund.qp2)
sum_fl.qp2 <- summary(weighted_fl_abund.qp2)
print(plot(weighted_fl_abund.qp2, allTerms = TRUE), pages = 4)
check2D(weighted_fl_abund.qp2, x1 = "yday", x2 = "elev.mean")

bb_abund.qp2 <- bam(bb.abund ~ 
                     s(bb.sp.ord, bs = "re") + # center species
                     s(year, bs = "re") + # random intercept for year
                     s(site, bs = "re") + # random intercept to avoid pseudoreplicating elevation
                     te(yday, elev.mean, # tensor product smooth of elevation and time
                        by = year, # by bb.sp
                        bs= c("gp", "tp"), # gaussian procees for time, thinplate spline for elevation
                        k=c(5, 5), 
                        m=2) +
                     te(yday, elev.mean, # tensor product smooth of elevation and time
                        by = bb.sp.ord, # by bb.sp
                        bs= c("gp", "tp"), # gaussian procees for time, thinplate spline for elevation
                        k=c(5, 5), 
                        m=2),
                   data = filter(bb_abund_sp, bb.sp != "humi"), # humi is just too rare
                   discrete = TRUE,
                   family = "quasipoisson",
                   select = TRUE,
                   method = "fREML") %>% getViz(nsim = 500)

check.gamViz(bb_abund.qp2)
sum.qp2 <- summary(bb_abund.qp2)
print(plot(bb_abund.qp2, allTerms = TRUE), pages = 4)
check2D(bb_abund.qp2, x1 = "yday", x2 = "elev.mean")
```
